---
title: "Week 9 Assignment"
author: "CHUN SHING LEUNG"
date: "2023-11-04"
output: html_document
---
## Assignment
The New York Times web site provides a rich set of APIs, as described here: https://developer.nytimes.com/apis

You’ll need to start by signing up for an API key. Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame.

## Libraries

```{r warning=FALSE, message=FALSE}
library(jsonlite)
library(tidyverse)
library(httr)

```

## Connecting API

Top Stories API is used. There are many sections available. Science section is selected.
https://developer.nytimes.com/docs/top-stories-product/1/overview


```{r}
# API Key
apikey <- "VFeXw5YKKBTWemlgGWuu1GlZm73D1TAM"

#URL
url <- "https://api.nytimes.com/svc/topstories/v2/science.json?api-key="

#GET
resp <- GET(paste(url, apikey, sep=""))
resp
summary(resp)

text_content <- content(resp, as = "text")

```
## From JSON data to an R dataframe

```{r}
data <- fromJSON(text_content)
df <- as.data.frame(data)

glimpse(df)

```

## Tidy the Data

```{r}
# select columns and rename them
df2 <- df |> 
        select(results.title, results.section, results.published_date) |> 
        rename(title = results.title, result_section = results.section, published_date = results.published_date)

# second row need to be removed as it has empty title
df2 <- df2[-2,]

```

## What is the most common result section under science section?

We can see Health related article is more common!!

```{r}
# Summary of result_section and its count
df3 <- df2 |> 
        group_by(result_section) |> 
        summarise(n = n())
df3

# Bar plot
ggplot(df3, aes(x = reorder(result_section, -n), y = n, fill = result_section)) +
geom_bar(stat = "identity") +
labs(title = "Common article section under Science Category",
     x = "Result section",
     y = "Count") +
theme_minimal()

```


