---
title: "Assigment_5_Answer"
author: "CHUN SHING LEUNG"
date: "2023-09-30"
output: html_document
---

(1) Create a .CSV file (or optionally, a MySQL database!) that includes all of the information above.
You’re encouraged to use a “wide” structure similar to how the information appears above, so
that you can practice tidying and transformations as described below.

(2) Read the information from your .CSV file into R, and use tidyr and dplyr as needed to tidy
and transform your data. 

```{r warning=FALSE, message=FALSE}
# Tidyverse packages includes ggplot2, dplyr, tidyr already
library(tidyverse)

table <- read.csv("https://raw.githubusercontent.com/tonyCUNY/tonyCUNY/main/assignment5.csv")

table

```

(2) Tidy and transform the data. 

```{r}
# Remove row with NA value
# Rename X and X.1 to Airline and Status
table_1 <- table |> 
              slice(-3) |>
              rename(Airline = X, Status = X.1)

```

```{r}
# Fill in the missing values under Airline column
table_1[2, 1] <- 'ALASKA'
table_1[4, 1] <- 'AM WEST'

table_1
```

```{r}
# Use pivot_longer() to transform all location into Destination column
# arrange by Destination column

table_2 <- table_1 |> 
  pivot_longer(
    cols = c("Los.Angeles", "Phoenix", "San.Diego", "San.Francisco", "Seattle"),
    names_to = "Destination",
    values_to = "Count"
  ) |> 
    arrange(Destination)

table_2

```
```{r}
# Use pivot_wider() to transform values under Status into two columns: On_time, Delayed
# value will be from Count column
# rename the new column

table_3 <- table_2 |> 
  pivot_wider(
    names_from = Status,
    values_from = Count,
  ) |> 
    rename(On_time = 'on time', Delayed = delayed)

table_3

```

```{r}
# Create a column: Delay_rate

table_4 <- table_3 |> 
            mutate(Delay_rate = round((Delayed / (On_time + Delayed)) * 100, 2))
table_4

```
(3) Perform analysis to compare the arrival delays for the two airlines

```{r}
# Create a table showing two airlines Delay_rate for each Destination

table_5 <- table_4 |> 
            group_by(Destination, Airline) |> 
            summarize(Delay_rate) |> 
            spread(Airline, Delay_rate) |> 
            rename(AM_WEST = 'AM WEST')
    
table_5

```

Conclusion: AM WEST has higher delay_rate than ALASKA

```{r}
# Visualize the results

table_4 |>
  group_by(Airline) |> 
      ggplot(aes(x = Destination, y = Delay_rate, fill = Airline)) +
      geom_bar(stat = "identity", position = "dodge") +
      labs(title = "Airline Arrival Delay",
        x = "Destination",
        y = "Delayrate (%)")

```
