---
title: "DATA607_Assignment_07"
author: "CHUN SHING LEUNG"
date: "2023-10-15"
output: html_document
---

Pick three of your favorite books on one of your favorite subjects. At least one of the books should have more
than one author. For each book, include the title, authors, and two or three other attributes that you find
interesting.
Take the information that you’ve selected about these three books, and separately create three files which
store the book’s information in HTML (using an html table), XML, and JSON formats (e.g. “books.html”,
“books.xml”, and “books.json”). To help you better understand the different file structures, I’d prefer that you
create each of these files “by hand” unless you’re already very comfortable with the file formats.

Write R code, using your packages of choice, to load the information from each of the three sources into
separate R data frames. Are the three data frames identical?

The three dataframe is slightly different on format.
For example, Json file will add "book." on all column.
the as.data.frame in XML will generate \n in all cell value which will take further step to remove


## Loading the packages

```{r setup, include=FALSE}
library(rvest)
library(xml2)
library(XML)
library(RCurl)
library(DT)
library(jsonlite)

```

## loading the HTML table from github

```{r}

html_file <- "https://raw.githubusercontent.com/tonyCUNY/tonyCUNY/main/Book.html"
html <- read_html(html_file)

table <- html |>  
          html_nodes("table") |> 
          html_table(fill = TRUE)

df <- as.data.frame(table)

df

```

## loading the xml table from github


```{r}

xmlurl <- getURL("https://raw.githubusercontent.com/tonyCUNY/tonyCUNY/main/book5.xml")
results <- xmlParse(xmlurl)
df2 <- xmlToDataFrame(results)
df3 <- as.data.frame(df2)
# \n shown in all cell value
# remove it by the following code:
df3[] <- lapply(df3, function(x) gsub("\n", "", x))
df3
```
## loading the json table from github

```{r}

json_file <- "https://raw.githubusercontent.com/tonyCUNY/tonyCUNY/main/book6.json"
json_data <- fromJSON(json_file)
df4 <- as.data.frame(json_data)
df4


```
