---
title: "Data 607 Week 3 Assignment"
author: "CHUN SHING LEUNG"
date: "2023-09-16"
output: html_document
---
## Library

```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(stringr)
library(dplyr)


```

## 1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r}

major_list <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv",header = TRUE, sep = ",")

head(major_list)

grep(pattern = 'data|statistics',major_list$Major, value = TRUE, ignore.case = TRUE)

```

## 2. Write code that transforms the data below:
[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"

Into a format like this:
c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r}

data1 <- '"bell pepper" "bilberry" "blackberry" "blood orange" "blueberry" "cantaloupe" "chili pepper" "cloudberry" "elderberry" "lime" "lychee" "mulberry" "olive" "salal berry"'

data2 <- strsplit(data1, " ")
data4 <- as.data.frame(data2)
head(data4)

```

#3 Describe, in words, what these expressions will match:
(.)\1\1
"(.)(.)\\2\\1"
(..)\1
"(.).\\1.\\1"
"(.)(.)(.).*\\3\\2\\1"


(.)\1\1: 
This shows the same character repeating three times. 

"(.)(.)\\2\\1": 
The shows a pair of characters and then it reverses the same pair of characters and put them at the end.

(..)\1: 
Any 2 characters repeated 1 time.

"(.).\\1.\\1": 
This shows 1 character and any character after it, And then, it shows the first 1 character followed by any character. Lastly, it shows the first character again. 

"(.)(.)(.).*\\3\\2\\1" 
This shows 3 characters and any character after it. It then shows the 3 characters again in reverse order. 

#4 Construct regular expressions to match words that:

Start and end with the same character.

```{r}

str_view("apple", "^(.)((.*\\1$)|\\1$)")

```
Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)

```{r}

str_view("church", "([A-Za-z][A-Za-z]).*\\1")

```
Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)

```{r}

str_view("eleven", "([A-Za-z]).*\\1.*\\1.")

```

