---
title: "Data 607 Week 2 Assignment"
author: "CHUN SHING LEUNG"
date: "2023-09-09"
output: html_document
---

## Library

```{r}
library(RMySQL)
library(DBI)

```

## Load th einformation from SQL database into an R dataframe

Assignment – SQL and R
Choose six recent popular movies. Ask at least five people that you know (friends, family, classmates, imaginary
friends if necessary) to rate each of these movies that they have seen on a scale of 1 to 5. Take the results
(observations) and store them in a SQL database of your choosing. Load the information from the SQL database
into an R dataframe.

The result can be accessed from my Github:
https://raw.githubusercontent.com/tonyCUNY/tonyCUNY/main/A2movierate.csv


```{r}
# Connect to MySQL and retrieve A2movierate dataset.

mydb = dbConnect(MySQL(), user='root', password='1234test', dbname='mr', host='localhost')
movie <- dbGetQuery(mydb, "select Name, movieId, rating from mr.A2movierate")
summary(movie)
head(movie)

```