---
title: "Data_607_Project_2_Dataset_2"
author: "CHUN SHING LEUNG"
date: "2023-10-15"
output: html_document
---

## Loading the dataset

The Second data set is NYPD Arrest Data in 2023 from NYC database.
https://data.cityofnewyork.us/Public-Safety/NYPD-Arrest-Data-Year-to-Date-/uip8-fykc

How's the number of arrest disturb among race, age and sex? Is there a peak month?

```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)

ny_arrest <- read_csv("https://raw.githubusercontent.com/tonyCUNY/tonyCUNY/main/NYPD_Arrest_Data__Year_to_Date__20231014.csv")

glimpse(ny_arrest)

```
## Data cleaning and transformation

```{r}
# drop all rows with NA value
# select column: ARREST_DATE, PD_DESC, AGE_GROUP, PERP_SEX, PERP_RACE, 
# create a new column and transform ARREST_DATE into month

ny_arrest2 <- ny_arrest |> 
                  drop_na() |> 
                  select(c(ARREST_DATE, PD_DESC, AGE_GROUP, PERP_SEX, PERP_RACE)) |>
                  mutate(MONTH = month(as.Date(ARREST_DATE, format = "%m/%d/%Y"))) |> 
                  relocate(MONTH, .after = ARREST_DATE)

head(ny_arrest2)

# 

```


## Summary for number of arrest by month, sex

```{r warning=FALSE, message=FALSE}

arrest_count <- ny_arrest2 |> 
                    group_by(PERP_RACE, AGE_GROUP, PERP_SEX) |> 
                    summarise(COUNT = n())
arrest_count

month_arrest_count <- ny_arrest2 |> 
                      group_by(MONTH, PERP_RACE, AGE_GROUP, PERP_SEX) |> 
                      summarise(COUNT = n())
month_arrest_count

write.csv(month_arrest_count, "C:\\Users\\tonyl\\Desktop\\CUNY\\arrest_count.csv", row.names = FALSE)

# 

```

## Visualize the data

No of arrest over different variable: PERP_RACE, AGE_GROUP, PERP_SEX AND MONTH
25-44 Age group has the highest number of arrest.
Mostly male are being arrested.
Black and white Hispanic have higher number of arrest. 
Each month has about the same number of arrest.

```{r warning=FALSE, message=FALSE}

# No of arrest by PERP_RACE AND MONTH
ny_arrest2 |> 
      group_by(PERP_RACE, MONTH) |> 
      summarise(COUNT = n()) |>
      ggplot(aes(x = MONTH, y = COUNT, fill = PERP_RACE)) +
      geom_bar(stat = "identity", position = "dodge") +
      labs(title = "Number of Arrests by PERP_RACE and MONTH", x = "MONTH", y = "Number of Arrests", fill = "PERP_RACE")

# No of arrest by PERP_RACE AND AGE_GROUP
ny_arrest2 |> 
      group_by(AGE_GROUP, PERP_RACE) |> 
      summarise(COUNT = n()) |>
      ggplot(aes(x = reorder(PERP_RACE, COUNT), y = COUNT, fill = AGE_GROUP)) +
      geom_bar(stat = "identity") + 
      coord_flip() +
      labs(title = "Number of Arrests by PERP_RACE", x = "PERP_RACE", y = "Number of Arrests")

# No of arrest by AGE_GROUP AND PERP_SEX
ny_arrest2 |> 
      group_by(PERP_SEX, AGE_GROUP) |> 
      summarise(COUNT = n()) |>
      ggplot(aes(x = reorder(AGE_GROUP, COUNT), y = COUNT, fill = PERP_SEX)) +
      geom_bar(stat = "identity") + 
      coord_flip() +
      labs(title = "Number of Arrests by AGE_GROUP", x = "AGE_GROUP", y = "Number of Arrests")

```


