---
title: "Data_607_Project_2_Dataset_1"
author: "CHUN SHING LEUNG"
date: "2023-10-14"
output: html_document
---

The first data set is USA real estate dataset from Kaggle.
https://www.kaggle.com/datasets/ahmedshahriarsakib/usa-real-estate-dataset

Which sate has the highest average house price and which city in this state has the biggest house?

```{r warning=FALSE, message=FALSE}
library(tidyverse)

realestate <- read_csv("~/data_607_project_2/realtor-data.csv")

head(realestate)

realestate

```

## Data cleaning and transformation

```{r}
# remove duplicate rows 
# drop all rows with NA value
# remove prev_sold_date, status and zip code column
# rename bed to bedroom
# relocate State, city to the front
realestate2 <- realestate |> 
                    distinct() |> 
                    drop_na() |> 
                    select(-c(status, prev_sold_date, zip_code)) |>
                    rename(bedroom = 'bed') |>
                    relocate(state, city)
realestate2
# 

```

## Examining what range of data is more common.

```{r}
# Summary to see number of bedroom, bath and house size in the narrowed data set

sum_bath <- realestate2 |> 
              group_by(bath) |> 
              summarise(n = n()) 
sum_bath
ggplot(sum_bath, aes(x = bath, y = n)) +
geom_bar(stat = "identity") +
scale_x_continuous(limits = c(0, 15)) +
labs(title = "Bathroom count",
     x = "Num of Bathroom",
     y = "Count")

sum_bed <- realestate2 |> 
              group_by(bedroom) |> 
              summarise(n = n())
sum_bed
ggplot(sum_bed, aes(x = bedroom, y = n)) +
geom_bar(stat = "identity") +
scale_x_continuous(limits = c(0, 15)) +
labs(title = "Bedroom count",
     x = "Num of Bedroom",
     y = "Count")

# 

```

## Further transforming the data base.

```{r}
# From the Bathroom count summary and plot, any house with bathroom more than 5 can be removed from the data as they are not common and can be considered as extreme observation.
# From the Bedroom count summary and plot, any house with bedroom more than 6 can be removed from the data as they are not common and can be considered as extreme observation.

# When the x axis scale is limited between 0 to 15, both plots show some rows contain missing value as well.

realestate3 <- realestate2 |> 
                  filter(bath < 6) |> 
                  filter(bedroom < 7)

realestate3 |> 
    group_by(bath) |> 
    summarise(n = n()) |> 
    ggplot(aes(x = bath, y = n)) +
    geom_bar(stat = "identity") +
    scale_x_continuous(limits = c(0, 6)) +
    labs(title = "Bathroom count",
         x = "Num of Bathroom",
         y = "Count")

realestate3 |> 
    group_by(bedroom) |> 
    summarise(n = n()) |> 
    ggplot(aes(x = bedroom, y = n)) +
    geom_bar(stat = "identity") +
    scale_x_continuous(limits = c(0, 8)) +
    labs(title = "Bedroom count",
         x = "Num of Bedroom",
         y = "Count")

```

## Visualize the data

New York has the highest Average house price!!
Glen Cove has the biggest house!!

```{r}

# Average price by Sate
avg_price_by_state <- realestate3 |> 
                        group_by(state) |> 
                        summarise(avg_price = mean(price))

ggplot(avg_price_by_state, aes(x = reorder(state, avg_price), y = avg_price)) +
  geom_bar(stat = "identity") + 
  coord_flip() +
  labs(title = "Average price by Sate",
       x = "State",
       y = "Average price")

# Top 10 expensive city in New York
avg_price_by_city <- realestate3 |>
                        filter(state == 'New York') |> 
                        group_by(city) |>
                        summarise(avg_price = mean(price))
                        

avg_price_by_city |> 
  top_n(10, avg_price) |> 
  ggplot(aes(x = reorder(city, avg_price), y = avg_price)) +
  geom_bar(stat = "identity") + 
  coord_flip() +
  labs(title = "Top 10 expensive city in New York",
       x = "City in New York State",
       y = "Average price")

# Top 10 city with biggest house in New York

avg_housesize_by_city <- realestate3 |>
                        filter(state == 'New York') |> 
                        group_by(city) |>
                        summarise(avg_size = mean(house_size))
                        

avg_housesize_by_city |> 
  top_n(10, avg_size) |> 
  ggplot(aes(x = reorder(city, avg_size), y = avg_size)) +
  geom_bar(stat = "identity") + 
  coord_flip() +
  labs(title = "Top 10 city with biggest house in New York",
       x = "City in New York State",
       y = "Average House size")


```

