---
title: "DATA 621"
author: "CHUN SHING LEUNG"
date: "2024-09-26"
output: html_document
---

```{r}
library(tidyverse)
library(kableExtra)
library(VIM)
```


1. DATA EXPLORATION (25 Points)

1. There are multiple variables with missing (NA) values, with TEAM-BATTING_HBP being the highest.


BATTING_HBP is showing very close mean and median vlaue -> because of less number of datapoints?.




```{r}
mtd <- read.csv("https://raw.githubusercontent.com/moham6839/Data_621_HW1/main/moneyball-training-data.csv")

med <- read.csv("https://raw.githubusercontent.com/moham6839/Data_621_HW1/main/moneyball-evaluation-data.csv")

glimpse(mtd)
```

MEAN, MEDIAN

```{r}
mtd %>%
  summary() %>%
  kable() %>%
  kable_styling()
```

Missing (NA) values: TEAM-BATTING_HBP has the highest missing values


```{r}
mtd %>% 
  gather(variable, value) %>%
  filter(is.na(value)) %>%
  group_by(variable) %>%
  tally() %>%
  arrange(desc(n)) %>%
  kable() %>%
  kable_styling()
```

PITCHING_H, PITCHING_BB, PITCHING_SO and FIELDING_E are extremely skewed
All skewed variables are right-skewed except BATTING_BB

```{r}
mtd %>%
  gather(variable, value, TARGET_WINS:TEAM_FIELDING_DP) %>%
  ggplot(., aes(value)) + 
  geom_histogram(fill = "indianred4", color="indianred4", bins = 30) + 
  facet_wrap(~variable, scales ="free", ncol = 4) +
  labs(x = element_blank(), y = element_blank())

```

Most of the independent variables have high variances
Medians and Means are quite different among them
It's clear it has outliers

```{r}
ggplot(stack(mtd), aes(x = ind, y = values)) +
  geom_boxplot() +
  coord_cartesian(ylim = c(0, 5000))+
  labs(x = element_blank(), y = element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

There were high correlations between batting and pitching stats that were measuring the same feature. For instance, homeruns (HR), Walks (BB), Strikeouts (SO), and Hits (H) for batting and pitching were highly correlated with their respective feature. This will be important to consider when selecting our features for modeling.


```{r}
cor_matrix <- mtd %>% 
  cor(., use = "complete.obs")

ggcorrplot::ggcorrplot(cor_matrix, type = "lower",
          lab = TRUE, lab_size = 2.1, tl.cex = 8)
```




```{r}
cor_matrix[lower.tri(cor_matrix, diag=TRUE)] <- ""
cor_matrix <- cor_matrix %>%
  as.data.frame() %>%
  rownames_to_column() %>%
  gather(Variable, Correlation, -rowname) %>%
  filter(Variable != rowname) %>%
  filter(Correlation != "") %>%
  mutate(Correlation = as.numeric(Correlation)) %>%
  rename(` Variable` = rowname) %>%
  arrange(desc(abs(Correlation))) 
```

```{r}
cor_matrix %>%
  filter(abs(Correlation) > .5) %>%
  kable() %>%
  kable_styling()
```

Response variable (TARGET_WINS) looks to be normally distributed = Good!

few variables with missing values = need to deal with.

Some variables are right skewed (TEAM_BASERUN_CS, TEAM_BASERUN_SB, etc.) = non-normally distributed residuals = Transform?

Dataset covers a wide time period spanning across multiple “eras” of baseball.


```{r}
mtd %>%
  gather(variable, value, -TARGET_WINS) %>%
  ggplot(., aes(value, TARGET_WINS)) + 
  geom_point(fill = "indianred4", color="indianred4") + 
  geom_smooth(method = "lm", se = FALSE, color = "black") + 
  facet_wrap(~variable, scales ="free", ncol = 4) +
  labs(x = element_blank(), y = "Wins")
```

4 DATA PREPARATION


Fixing Missing/Zero Values
Remove the invalid data and prepare it for imputatio = TEAM_BATTING_HBP is missing over 90% of its values. That variable will be removed completely.

```{r}

#Replace 0 with NA for Imputing 
#Replace high TEAM_PITCHING_SO values with NA for Imputing 

mtd2 <- mtd |> 
          select(-TEAM_BATTING_HBP) |> 
          mutate(TEAM_BATTING_SO = ifelse(TEAM_BATTING_SO == 0, NA, TEAM_BATTING_SO)) |> 
          mutate(TEAM_PITCHING_SO = ifelse(TEAM_PITCHING_SO > 4374, NA, TEAM_PITCHING_SO))

med2 <- med |> 
          select(-TEAM_BATTING_HBP) |> 
          mutate(TEAM_BATTING_SO = ifelse(TEAM_BATTING_SO == 0, NA, TEAM_BATTING_SO)) |> 
          mutate(TEAM_PITCHING_SO = ifelse(TEAM_PITCHING_SO > 4374, NA, TEAM_PITCHING_SO))

```

Imputing the values using KNN:

