---
title: "Data_607_Project_3"
output: html_document
date: "2023-10-28"
---

## Project 3 Team Members
Ariann Chai
Chun Shing Leung 
Lwin Shwe  
 

## The data used to answer the question is "Netflix TV Shows and Movies" from Kaggle.

This data set listed all shows available on Netflix streaming. It was acquired in July 2022 containing data available in the United States.

Source: https://www.kaggle.com/datasets/victorsoeiro/netflix-tv-shows-and-movies/code

   What are the top 10 movies with highest scores?  
   Which movies have large amount of voters?  
   How these information change across countries, years, ages and genres?  

```{r warning=FALSE, message=FALSE}
library(tidyverse)

url <- "https://raw.githubusercontent.com/tonyCUNY/tonyCUNY/main/titles2.csv"

netflix <- read_csv(url, col_names = TRUE)

head(netflix)

```

## Data Exploration

There are 5850 rows and 15 columns in this data set
There are 2106 shows and 3744 movies
There are 8167 missing values in this data set
Each column missing values are listed. Please see below.
No observations are duplicated


```{r}
glimpse(netflix)
summary(netflix)
show_count <- sum(netflix$type == "SHOW")
movie_count <- sum(netflix$type == "MOVIE")
total_na <- sum(is.na(netflix))
print(show_count)
print(movie_count)
print(total_na)
netflix |> 
  summarise(across(everything(), ~ sum(is.na(.)))) |>
  t()
nrow(netflix[duplicated(netflix),])


```

## Data Cleaning and transformation

The NA values for title column can be removed as it doesn't refer to any movie or show.
Some NA values under age_certification, score, votes can be kept as removing them will take up too much information from this data
Some column such as id, description, seasons, imdb_id are not useful to our anaylsis. They can be removed.
Production_countries column need to be cleared up.
Preparing a new set of data frame so Genres column are broken down by genres value.

```{r}

# Drop NA values for title column
# Drop id, description, seasons, imdb_id column
# Any production countries with multiple location is renamed as "GLOBAL"
# Clean the production_countries column by removing the bracket
# There are empty values under production_countries. They are removed as well

netflix_clean <- netflix |> 
                    filter(!is.na(title)) |> 
                    select(-c(id, description, seasons, imdb_id)) |> 
                    mutate(production_countries = ifelse(grepl(",", production_countries), "GLOBAL", production_countries)) |> 
                    mutate(production_countries = str_extract_all(production_countries,"[A-Za-z]+") |> sapply(toString) ) |> 
                    filter(production_countries != "")

# Take a look of the cleaned data

glimpse(netflix_clean)
netflix_clean |> 
  summarise(across(everything(), ~ sum(is.na(.)))) |>
  t()

# Clean genre column 
# Remove the brackets and the quotes
# Separate genres type
# Remove empty values

netflix_genres <- netflix_clean |> 
                    mutate(genres = gsub("\\[|\\]|'", "", genres)) |> 
                    separate_rows(genres, sep = ",\\s*") |> 
                    filter(!is.na(genres) & genres != "")

glimpse(netflix_genres)

```


## Data Analysis and Visualization 

  What are the top 10 movies with highest scores?  
  Which movies have large amount of voters?  
  How these information change across countries, years, ages and genres?
  Age Certifications Count
  Genres Count
  
```{r}
result <- netflix_genres %>%
  group_by(type, genres) %>%
  summarise(GenreCount = n())
result
```

## Conclusion
## Which are the most valued data science skills?

