---
title: "Project 1"
author: "CHUN SHING LEUNG"
date: "2023-09-23"
output: html_document
---

In this project, you’re given a text file with chess tournament results where the information has some structure. Your job is to create an R Markdown file that generates a .CSV file (that could for example be imported into a SQL database) with the following information for all of the players:

Player’s Name, 
Player’s State, 
Total Number of Points, 
Player’s Pre-Rating, 
Average Pre Chess Rating of Opponents


## Loading the Text File

```{r warning=FALSE, message=FALSE}
library(stringr)
library(readr)
library(dplyr)


theUrl <- 'https://raw.githubusercontent.com/tonyCUNY/tonyCUNY/main/tournamentinfo.txt'

# Reading the data again but skip the first 4 lines

df2 <- read.table(file=theUrl, skip = 4, sep=",")

```

## Reading the data. 

```{r}
# Inspect the data structure.

head(df2)

```

## Extracting the data part 1.

Here are the steps I use to extract the information for just 1 player- GARY HUA:

1. The first 4 lines are not needed. They are removed.

2. Use strsplit to split elements according to matches "|" and space (\\s*) around it.

   Results are stored in sub_n1, sub_n2.
   
3. Transform sub_n1, sub_n2 as data.frame so each elements are stored in different rows.

4. Id, Name, State, Number of Points, Pre-Rating can be accessed individually from specific row

5. Use str_extract and regex to extract the information we need. 

```{r}
# split elements according to matches "|" and space (\\s*) around it
sub_n1 <- strsplit(df2[1, ], "\\s*\\|\\s*")
sub_n2 <- strsplit(df2[2, ], "\\s*\\|\\s*")
sub_n1
sub_n2

# Transform sub_n1, sub_n2 as data.frame
sub_n1_df <- as.data.frame(sub_n1)
sub_n2_df <- as.data.frame(sub_n2)

# Access Id, Name, State, Number of Points, Pre-Rating
# Player's ID - It will be used when calcuating the Average Pre Chess Rating
str_extract(sub_n1_df[1,], "\\d+")
# Player’s Name
sub_n1_df[2,]
# Player’s State
str_extract(sub_n2_df[1, ], "\\b[A-Z]+\\b")
# Total Number of Points
sub_n1_df[3,]
# Player’s Pre-Rating
str_extract(sub_n2_df[2,], "(?<=R: )\\d+")
# Opponents ID 1 - 7
str_extract(sub_n1_df[4,], "\\d+")
str_extract(sub_n1_df[5,], "\\d+")
str_extract(sub_n1_df[6,], "\\d+")
str_extract(sub_n1_df[7,], "\\d+")
str_extract(sub_n1_df[8,], "\\d+")
str_extract(sub_n1_df[9,], "\\d+")
str_extract(sub_n1_df[10,], "\\d+")


```

## Extracting the data part 2.

Now we need to use a loop to repeat part 1 to extract information from all players.

Create a simple for loop to extract elements in a list and combine them into a new vector

test <- c()

for (i in 1:length(test_list)) {

  test <- c(test, test_list[[i]])
  
}

Expand this loop to include all the vectors we need.

Function Seq() will tell the for loop which row to access.

item 1. Row contains ID, Name, Number of Points, Opponents ID repeat every 3 lines

item 2. Row contains State, Pre-Rating repeat every 3 lines

```{r}
# Use loop to repeat part 1 and complete item 1

id = c()
name = c()
total_num_points = c()
o1 = c()
o2 = c()
o3 = c()
o4 = c()
o5 = c()
o6 = c()
o7 = c()

for (i in seq(1, nrow(df2), by = 3)) {
  sub = as.data.frame(strsplit(df2[i, ], "\\s*\\|\\s*"))
  id = c(id, as.numeric(str_extract(sub[1,], "\\d+")))
  name = c(name, sub[2,])
  total_num_points = c(total_num_points, sub[3,])
  o1 = c(o1, as.numeric(str_extract(sub[4,], "\\d+")))
  o2 = c(o2, as.numeric(str_extract(sub[5,], "\\d+")))
  o3 = c(o3, as.numeric(str_extract(sub[6,], "\\d+")))
  o4 = c(o4, as.numeric(str_extract(sub[7,], "\\d+")))
  o5 = c(o5, as.numeric(str_extract(sub[8,], "\\d+")))
  o6 = c(o6, as.numeric(str_extract(sub[9,], "\\d+")))
  o7 = c(o7, as.numeric(str_extract(sub[10,], "\\d+")))
}

# Use loop to repeat part 1 and complete item 2

state = c()
pre_rating = c()

for (i in seq(2, nrow(df2), by = 3)) {
  sub = as.data.frame(strsplit(df2[i, ], "\\s*\\|\\s*"))
  state = c(state, str_extract(sub[1, ], "\\b[A-Z]+\\b"))
  pre_rating = c(pre_rating, as.numeric(str_extract(sub[2,], "(?<=R: )\\d+")))
  
}


```

## Combine all the vectors into the a dataframe

```{r}

table = data.frame(id, state, name, total_num_points, pre_rating, o1, o2, o3, o4, o5, o6, o7 )

head(table)

```

## Find out Average Pre Chess Rating of Opponents

Now we need to calculate Average Pre Chess Rating of Opponents and create a new column Avg_Chess_Rate 

The values of o1, 2, 3, 4, 5, 6, 7 are referring to values of ID

They are used to call out the pre_rating value corresponding to the matched ID:

For example, table\$pre_rating[table$id[table[1, 6]] = 39 

!is.na is used to filter out NA value during the loop.

The count2 column under total4 is to get us correct denominator value.Because some players play less then 7

games.

```{r}

col_index <- c(6, 7, 8, 9, 10, 11, 12)
total4 <- data.frame(total1 = rep(0, 64),
                     count2 = rep(0, 64))


for (i in 1:64) {
  for (j in col_index) {
    if (!is.na(table$pre_rating[table$id[table[i, j]]])) {
      total4[i, 1] <- total4[i, 1] + table$pre_rating[table$id[table[i, j]]]
    }
    if (is.na(table[i, j])) {
      total4[i, 2] <- total4[i, 2] + 1
    }
  }
}


Avg_Chess_Rate <- c()

for (i in 1:64) {
  Avg_Chess_Rate[i] <- total4[i, 1] / (7 - total4[i, 2])
}

result_avg = as.data.frame(Avg_Chess_Rate)
head(result_avg)


```

## Built the final table and export it CSV file.



```{r}

final_table <- cbind(table, result_avg)
head(final_table)
final_table2 <- data.frame(final_table$name, final_table$state, final_table$pre_rating, final_table$Avg_Chess_Rate)
head(final_table2)

write.csv(final_table, "C:\\Users\\tonyl\\Desktop\\CUNY\\final_table.csv", row.names = FALSE)
write.csv(final_table2, "C:\\Users\\tonyl\\Desktop\\CUNY\\final_table2.csv", row.names = FALSE)
```

