---
title: "Week_10_Assignment"
author: "CHUN SHING LEUNG"
date: "2023-11-13"
output: html_document
---

In Text Mining with R, Chapter 2 looks at Sentiment Analysis.  In this assignment, you should start by getting the primary example code from chapter 2 working in an R Markdown document.  You should provide a citation to this base code.  You’re then asked to extend the code in two ways:

Work with a different corpus of your choosing, and

Incorporate at least one additional sentiment lexicon (possibly from another R package that you’ve found through research).

The base code for this assignemnet is from chapter 2 of Text Mining with R: A Tidy Approach

https://www.tidytextmining.com/sentiment.html

## Library

```{r  warning=FALSE, message=FALSE}
library("tidyverse")
library("janeaustenr")
library("stringr")
library("tidytext")

get_sentiments("afinn")
get_sentiments("bing")
get_sentiments("nrc")

```

## Sentiment Analysis with inner join


```{r  warning=FALSE, message=FALSE}
# Tokenize the data
tidy_books <- austen_books() %>%
  group_by(book) %>%
  mutate(
    linenumber = row_number(),
    chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]",
      ignore_case = TRUE
    )))
  ) %>%
  ungroup() %>%
  unnest_tokens(word, text)

# The nrc lexicon

nrc_joy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

tidy_books %>%
  filter(book == "Emma") %>%
  inner_join(nrc_joy) %>%
  count(word, sort = TRUE)

# The bing lexicon

jane_austen_sentiment <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(book, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)

# Visualization

ggplot(jane_austen_sentiment, aes(index, sentiment, fill = book)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~book, ncol = 2, scales = "free_x")



```

## Comparing the three sentiment dictionaries

```{r  warning=FALSE, message=FALSE}
# Filter out Pride and Prejudice from book

pride_prejudice <- tidy_books %>%
  filter(book == "Pride & Prejudice")

pride_prejudice

afinn <- pride_prejudice %>%
  inner_join(get_sentiments("afinn")) %>%
  group_by(index = linenumber %/% 80) %>%
  summarise(sentiment = sum(value)) %>%
  mutate(method = "AFINN")

bing_and_nrc <- bind_rows(
  pride_prejudice %>%
    inner_join(get_sentiments("bing")) %>%
    mutate(method = "Bing et al."),
  pride_prejudice %>%
    inner_join(get_sentiments("nrc") %>%
      filter(sentiment %in% c(
        "positive",
        "negative"
      ))) %>%
    mutate(method = "NRC")
) %>%
  count(method, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)

bind_rows(
  afinn,
  bing_and_nrc
) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")

get_sentiments("nrc") %>%
  filter(sentiment %in% c(
    "positive",
    "negative"
  )) %>%
  count(sentiment)

get_sentiments("bing") %>%
  count(sentiment)

```

## Most common positive and negative words

```{r  warning=FALSE, message=FALSE}

# Find out how much each word contributed to each sentiment.

bing_word_counts <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bing_word_counts

bing_word_counts %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(
    y = "Contribution to sentiment",
    x = NULL
  ) +
  coord_flip()

custom_stop_words <- bind_rows(tibble(word = c("miss"),  
                                      lexicon = c("custom")), 
                               stop_words)

custom_stop_words

```

## Wordclouds

```{r  warning=FALSE, message=FALSE}

library(wordcloud)

tidy_books %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))

library(reshape2)

tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"),
                   max.words = 100)

```

## Looking at units beyond just words 


```{r  warning=FALSE, message=FALSE}

p_and_p_sentences <- tibble(text = prideprejudice) %>% 
  unnest_tokens(sentence, text, token = "sentences")

p_and_p_sentences$sentence[2]

austen_chapters <- austen_books() %>%
  group_by(book) %>%
  unnest_tokens(chapter, text, token = "regex", 
                pattern = "Chapter|CHAPTER [\\dIVXLC]") %>%
  ungroup()

austen_chapters %>% 
  group_by(book) %>% 
  summarise(chapters = n())

bingnegative <- get_sentiments("bing") %>% 
  filter(sentiment == "negative")

wordcounts <- tidy_books %>%
  group_by(book, chapter) %>%
  summarize(words = n())

tidy_books %>%
  semi_join(bingnegative) %>%
  group_by(book, chapter) %>%
  summarize(negativewords = n()) %>%
  left_join(wordcounts, by = c("book", "chapter")) %>%
  mutate(ratio = negativewords/words) %>%
  filter(chapter != 0) %>%
  slice_max(ratio, n = 1) %>% 
  ungroup()

```


## Work with a different corpus of your choosing and incorporate at least one additional sentiment lexicon (possibly from another R package that you’ve found through research).

"Jane Eyre" by Charlotte Brontë will be used.

The Gutenberg ID for "Jane Eyre" is 1260

```{r  warning=FALSE, message=FALSE}

library(gutenbergr)

jane_eyre <- gutenberg_download(1260)

# Tokenize the data
tidy_jane <- jane_eyre %>%
                mutate(linenumber = row_number(), chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]", ignore_case = TRUE)))) %>%
                unnest_tokens(word, text)

# The nrc lexicon

fear <- get_sentiments("nrc") %>% 
            filter(sentiment == "fear")

jane_sentiment1 <- tidy_jane %>%
                      inner_join(fear) %>%
                      count(word, sort = TRUE)
jane_sentiment1 

# The bing lexicon

word_totals <- tidy_jane %>%
                    group_by(chapter) %>%
                    count()

jane_sentiment2 <- tidy_jane %>%
                    inner_join(get_sentiments("bing")) %>%
                    group_by(chapter) %>%
                    count(sentiment) %>%
                    filter(sentiment == 'negative') %>%
                    transform(p = n / word_totals$n) %>%
                    arrange(desc(p))
jane_sentiment2



# English sentiment lexicon created for use with financial documents. This lexicon labels words with six possible sentiments important in financial contexts: "negative", "positive", "litigious", "uncertainty", "constraining", or "superfluous".

# Append a column representing the proportion of positive words used

jane_sentiment3 <- tidy_jane %>%
                    inner_join(get_sentiments("loughran")) %>%
                    group_by(chapter) %>%
                    count(sentiment) %>%
                    filter(sentiment == 'positive') %>%
                    transform(p = n / word_totals$n) %>%
                    arrange(desc(p))

jane_sentiment3

# Bar plot - Positive Sentiment in Jane Eyre by Chapter 

ggplot(jane_sentiment3, aes(x = reorder(factor(chapter), -n), y = n, fill = factor(chapter))) +
  geom_bar(stat = "identity", color = "white") +
  labs(x = "Chapter", y = "Proportion of positive words used") +
  ggtitle("Positive Sentiment in Jane Eyre by Chapter") +
  theme_minimal() +
  theme(legend.position = "none")


```